CSCM37: Data Visualisation
Assignment 1
Andrew Gray
445348


Part 1 - A Real-World Challange 


Design 1

Image: The visualization itself as an image
 
Visual Design Type: Gantt

Name of Tool: Tableua Desktop

Country: All countries are shown.

Year: Between the years 1896 and 2018

Visual Mappings: The x coordinates are made up of the year that the power plant was commissioned, and the y coordinates are made up of the primary fuels of the commissioned power plants. 



Unique Observation: Things we can learn from the visualization, e.g, from this visualization we can see this pattern. . .

The oldest powerplant was commissioned in the USA in 1896 and its main fuel type was hydo. The second commissioned powerplant was also in the USA and again this was hydo which was commissioned in the 1899. Then in 1900 3 power plants were commissioned. These were Brazil
Data Preparation: There was no modifications made to this  
A good observation requires interpretation of the resulting image that you generate. 

Design 2

 




Design 5



Is this a task?? 
What is better? 


Part 2: More Depth 
Image: the treemap image you are describing
• Name of Tool: The tool that was used to generate the treemap
• Country: Name of country(s) data shown
• Year: the year(s) or time-span of data shown
• Data Preparation: A helpful description of how you prepared the data • Color: what is color mapped to?
• Hierarchy: What is the data hierarchy contained in the treemap?
• What leaf node size is mapped to?
• How are the leaf nodes laid out or positioned?
• What are internal nodes mapped to?
• What is internal node size mapped to?
• Which treemap node layout algorithm is used? 
Some of these questions may require some research or extra background reading to answer. The data set used must contain at least 1,000 data records (rows). Also, you may not simply re-use a treemap from part 1. If you used a treemap in part 1, then create a different one for part 2. 

Part 3: Getting Professional Help
VisGuides.org Username: AndyGray87
 
Question Posted with citation of paper: Add screen shot

Question Response.
Q’s to ask.
Does my visual design make sense?
• Is my choice of color map optimal?
• How can my visual design be improved? 
Are there any other types of visual layouts that would be better for this challenge? 
How else could I visualize the relationships between countries? 

1)	your description,

  
2) your image,
3) your question and
4) your Visuguides.org username. 

References

Andrews, Keith, and Martin Lessacher. 2010. “Liquid Diagrams: Informa- tion Visualisation Gadgets.” 2010 14th International Conference Information 
Visualisation, 104–9. https://doi.org/10.1109/IV.2010.100. Geng, Zhao, Robert S. Laramee, Fernando Loizides, and George Buchanan. 2011. 
“Visual Analysis of Document Triage Data.” In Proceedings of the International Conference on Imaging Theory and Applications and International Conference on Information Visualization Theory and Applications, 1:151–63. Algrave, Portugal. https://doi.org/10.5220/0003320401510163. 
Ward, Matthew O., Georges Grinstein, and Daniel Keim. 2015. Interactive Data Visualization: Foundations, Techniques, and Applications, Second Edition - 360 Degree Business. 2nd ed. USA: A. K. Peters, Ltd. 


remote: warning: File iOS Bootcamp/App Brewery Massive Bundle/PSD UI Designs/Funky Tunes/Free Sample.psd is 50.96 MB; this is larger than GitHub's recommended maximum file size of 50.00 MB        
remote: error: GH001: Large files detected. You may want to try Git Large File Storage - https://git-lfs.github.com.        
remote: error: Trace: a69c919f8f7b5f5605c8db968db69ed4        
remote: error: See http://git.io/iEPt8g for more information.        
remote: error: File iOS Bootcamp/iOS Zip Files Original/atom-mac.zip is 278.77 MB; this exceeds GitHub's file size limit of 100.00 MB        
remote: error: File iOS Bootcamp/App-Brewery-Massive-Bundle.zip is 590.38 MB; this exceeds GitHub's file size limit of 100.00 MB        
To https://github.com/codingWithAndy/Bootcamps.git
 ! [remote rejected] master → master (pre-receive hook declined)
